Dynein walks like an Imperial AT-ST

### 2018-02-28 papers/paper/paper.tex

\begin{figure*}[tbhp]
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_static_step_length_histogram}
    \subcaption{Static unbinding rate}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_exponential_step_length_histogram}
    \subcaption{Exponential unbinding rate}
  \end{subfigure}
\caption{Histogram of size of steps taken by model.}
\label{fig:lengthhist}
\end{figure*}

\begin{table}[tbhp]
\centering
\caption{Parameters used in model simulation.}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
$L_s$ & $\ls nm$ & \cite{nativestructure} & \\
$L_t$ & $\lt nm$ & \cite{nativestructure} & \\
$\theta_b$ & $\eqb$ &  & \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
$\theta_t$ & $\eqt$ &  & \\

>>>>

\begin{figure*}[tbhp]
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_static_step_length_histogram}
    \subcaption{Static unbinding rate}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_exponential_step_length_histogram}
    \subcaption{Exponential unbinding rate}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_static_foot_order_histogram}
    \subcaption{Static unbinding rate}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_exponential_foot_order_histogram}
    \subcaption{Exponential unbinding rate}
  \end{subfigure}
\caption{Stepping behavior of static and exponential models, with parameters shown in Table \ref{tab:staticparams}.}
\label{fig:lengthhist}
\end{figure*}

\begin{table}[tbhp]
\centering
\caption{Parameters used in model simulation.}
\label{tab:staticparams}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & 2.0 & \\
$L_s$ & $\ls nm$ & & \cite{nativestructure}\\
$L_t$ & $\lt nm$ & & \cite{nativestructure}\\
$\theta_b$ & $\eqb$ &  & \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  & \\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ &  & \\
$\theta_t$ & $\eqt$ &  & \\
